Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance

### 2017-05-09 pre_post_biorxiv.tex
Edit Acknowledgements

After offspring mortality, $\rho$ adult immigrants are added to the focal population. The kinship between an immigrant and all other individuals always equals zero ($k_{ij}=0$). Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations. To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry or pre-copulatory or post-copulatory inbreeding avoidance, immigrants are always male. Consequently, they can be chosen as females' mates based on their values of $k_{ij}=0$ but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$. Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values. We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ \cite[][]{@Duthie; @Duthie2016a}.

@@

This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen. We thank Matthew E. Wolak for very helpful comments on this manuscript.

>>>>

After offspring mortality, $\rho$ adult immigrants are added to the focal population. The kinship between an immigrant and all other individuals always equals zero ($k_{ij}=0$). Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations. To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry or pre-copulatory or post-copulatory inbreeding avoidance, immigrants are always male. Consequently, they can be chosen as females' mates based on their values of $k_{ij}=0$ but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$. Further, immigrants' $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration, meaning that they do not directly cause any change in the distribution of allele values. We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$ \cite[][]{Duthie, Duthie2016a}.

@@

This work was funded by a European Research Council Starting Grant to JMR. Computer simulations were performed using the Maxwell Computing Cluster at the University of Aberdeen. We thank Matthew E. Wolak for very helpful comments.
